A comprehensive framework to capture the arcana of neuroimaging analysis

### 2018-10-11 manuscript/manuscript.tex
created latex version of manuscript

\hypertarget{a-comprehensive-framework-to-capture-the-arcana-of-neuroimaging-analysis}{%
\section{A comprehensive framework to capture the arcana of neuroimaging
analysis}\label{a-comprehensive-framework-to-capture-the-arcana-of-neuroimaging-analysis}}

Thomas G. Close\textsuperscript{1,2},
Phillip G. D. Ward\textsuperscript{1,3,4},
Francesco Sforazzini\textsuperscript{1},
Wojtek Goscinski\textsuperscript{6},
Zhaolin Chen\textsuperscript{1,5},
Gary F. Egan\textsuperscript{1,3,4}

1. Monash Biomedical Imaging, Monash University, Melbourne, Australia

2. Australian National Imaging Facility, Australia

3. Australian Research Council Centre of Excellence for integrative
Brain Function, Melbourne, Australia

4. Monash Institute of Cognitive and Clinical Neurosciences, Monash
University, Melbourne, Australia.

5. Department of Electrical and Computer Systems Engineering, Monash
University, Melbourne, Australia

6. Monash eResearch Centre, Monash University, Melbourne, Australia

\hypertarget{introduction}{%
\section{Introduction}\label{introduction}}

Despite the availability of well-established neuroimaging analysis
packages (Cox 1996; Smith et. al. 2004; Friston et. al. 2007; Tournier
et. al. 2012), the arcana of neuroimaging analysis is substantial due to
the range of available tools, tunable parameters, and imaging sequences
involved (Cusack et. al. 2015). The distribution of complete
``end-to-end'' workflows, from acquired data to publication results, is
necessary for routine reproduction because of the effort required to
accurately exactly reimplement such analyses (Kennedy 2018). It is also
difficult to adapt existing workflows to new studies without detailed
knowledge of their design. Therefore, flexible, portable and complete
workflows are important to promote reproduction and code reuse in
neuroimaging research.

@@

\hypertarget{methods}{%
\section{Methods}\label{methods}}

\hypertarget{framework-overview}{%
\subsection{Framework overview}\label{framework-overview}}

@@

\includegraphics[width=3.55074in,height=3.16146in]{media/image23.png}

@@

\includegraphics[width=6.27083in,height=3.15278in]{media/image33.png}

@@

\hypertarget{analysis-design-study-classes}{%
\subsection{Analysis design: Study
classes}\label{analysis-design-study-classes}}

@@

\hypertarget{data-and-parameter-specification-tables}{%
\subsubsection{Data and parameter specification
tables}\label{data-and-parameter-specification-tables}}

@@

\includegraphics[width=5.74851in,height=6.07813in]{media/image27.png}

@@

\hypertarget{workflow-design}{%
\subsubsection{Workflow design}\label{workflow-design}}

@@

\includegraphics[width=5.33854in,height=4.21623in]{media/image35.png}

@@

The syntax for workflow graph construction in Arcana is inspired by the
proposed format for Nipype v2.0
(\href{https://github.com/nipy/nipype/issues/2539}{{https://github.com/nipy/nipype/issues/2539}}),
and will be updated as Nipype v2.0 is developed and upstream
functionality becomes available. Workflow nodes are created from Nipype
interfaces using the \emph{Pipeline.add(name, interface)} method of the
Pipeline should be used. Once created, the inputs of the node can be set
explicitly via the node's \emph{inputs} attribute, connected to other
nodes with the \emph{Pipeline.connect(out\_node, out\_node\_output,
in\_node, in\_node\_input)} method, or connected to inputs of the
pipeline. Pipeline inputs and outputs are connected to nodes using the
\emph{Pipeline.add\_input(spec\_name, node, node\_input)} and
\emph{Pipeline.add\_output(spec\_name, node, node\_output)} methods,
respectively.

@@

\includegraphics[width=6.27083in,height=2in]{media/image7.png}

@@

\hypertarget{extension-and-specialisation-by-class-inheritance}{%
\subsubsection{Extension and specialisation by class
inheritance}\label{extension-and-specialisation-by-class-inheritance}}

@@

\hypertarget{implementing-multi-modal-studies}{%
\subsubsection{Implementing multi-modal
studies}\label{implementing-multi-modal-studies}}

@@

\includegraphics[width=3.86429in,height=4.70313in]{media/image20.png}

@@

\includegraphics[width=6.27083in,height=4.69444in]{media/image21.png}

@@

\includegraphics[width=6.27083in,height=3.94444in]{media/image36.png}\textbf{Figure
8} - Example application of Study class to a dataset stored in an XNAT
repository. Once the Study object has been initialised potential
derivatives of the Study can be requested, and will be generated and
stored in the repository if already present.

@@

\hypertarget{study-inputs}{%
\subsubsection{Study inputs}\label{study-inputs}}

@@

\hypertarget{processor-modules}{%
\subsubsection{Processor modules}\label{processor-modules}}

@@

\hypertarget{results}{%
\section{Results}\label{results}}

@@

\includegraphics[width=3.82849in,height=6.85938in]{media/image28.png}

@@

\includegraphics[width=4.29167in,height=7.43818in]{media/image32.png}

@@

\includegraphics[width=6.228in,height=4.72396in]{media/image22.png}

@@

\includegraphics[width=6.27083in,height=4.18056in]{media/image34.png}

@@

\includegraphics[width=6.27083in,height=2.09722in]{media/image30.png}

@@

\hypertarget{discussion}{%
\section{Discussion}\label{discussion}}

@@

\hypertarget{conclusion}{%
\section{Conclusion}\label{conclusion}}

@@

\hypertarget{references}{%
\section{References}\label{references}}

Abadi, M., Barham, P., Chen, J., Chen, Z., Davis, A., Dean, J., Devin,
M., Ghemawat, S., Irving, G., Isard, M., Kudlur, M., Levenberg, J.,
Monga, R., Moore, S., Murray, D. G., Steiner, B., Tucker, P., Vasudevan,
V., Warden, P., Wicke, M., Yu, Y., Zheng, X.. (2016). TensorFlow: A
System for Large-Scale Machine Learning TensorFlow: A system for
large-scale machine learning. \emph{12th USENIX Symposium on Operating
Systems Design and Implementation (OSDI '16)}, 265--284.
\href{https://doi.org/10.1038/nn.3331}{{https://doi.org/10.1038/nn.3331}}

Achterberg, H. C., Koek, M., \& Niessen, W. J. (2016). Fastr: A Workflow
Engine for Advanced Data Flows in Medical Image Analysis.
\emph{Frontiers in ICT}, 3(August), 1--11.
\href{https://doi.org/10.3389/fict.2016.00015}{{https://doi.org/10.3389/fict.2016.00015}}

Amstutz, P., Crusoe, M. R., Tijanić, N., Chapman, B., Chilton, J.,
Heuer, M., Kartashov, A., Leehr, D., Ménager, H., Nedeljkovich, M.,
Scales, M., Soiland-Reyes, S., Stojanovic, L. (2016). Common workflow
language, v1. 0. Figshare.
doi:\href{https://doi.org/10.6084/m9.figshare.3115156.v2}{{10.6084/m9.figshare.3115156.v2}}

Avants, B. B., Tustison, N. J., Song, G., Cook, P. A., Klein, A., \&
Gee, J. C. (2011). A reproducible evaluation of ANTs similarity metric
performance in brain image registration. \emph{NeuroImage},
\emph{54}(3), 2033--2044.
\href{https://doi.org/10.1016/J.NEUROIMAGE.2010.09.025}{{https://doi.org/10.1016/J.NEUROIMAGE.2010.09.025}}

Book, G. A., Anderson, B. M., Stevens, M. C., Glahn, D. C., Assaf, M.,
\& Pearlson, G. D. (2013). Neuroinformatics Database (NiDB)--a modular,
portable database for the storage, analysis, and sharing of neuroimaging
data. \emph{Neuroinformatics}, \emph{11}(4), 495-505.

Cox, R. W. (1996): AFNI: Software for analysis and visualization of
functional magnetic resonance neuroimages. \emph{Computers and
Biomedical Research}, 29:162-173.

Cusack R., Vicente-Grabovetsky A., Mitchell D.J., Wild C.J., Auer T.,
Linke A.C., Peelle J.E. (2015) Automatic analysis (aa): Efficient
neuroimaging workflows and parallel processing using Matlab and XML.
\emph{Frontiers in Neuroinformatics} 8:90.

Das, S., Zijdenbos, A. P., Harlap, J., Vins, D., \& Evans, A. C. (2012).
LORIS: a web-based data management system for multi-center studies.
\emph{Frontiers in Neuroinformatics}, 5(January), 1--11.
\href{https://doi.org/10.3389/fninf.2011.00037}{{https://doi.org/10.3389/fninf.2011.00037}}

Esteban O. (2018) FMRIPrep: a robust preprocessing pipeline for
functional MRI. \emph{bioRxiv.} 306951;
doi:\href{https://doi.org/10.1101/306951}{{10.1101/306951}}

Friston K. (2007): Statistical parametric mapping. In:.
\emph{Statistical Parametric Mapping}. Elsevier. pp 10--31.

Furlani, J. (1991). Modules: Providing a flexible user environment.
\emph{Proceedings of the Fifth Large Installation Systems Administration
Conference (LISA V)}, (1), 141--152.

Gorgolewski K.J. et al. (2011), `Nipype: A Flexible, Lightweight and
Extensible Neuroimaging Data Processing Framework in Python'.
\emph{Frontiers in Neuroinformatics}, vol. 5.

Gorgolewski K. J. et al. (2016): `The brain imaging data structure, a
format for organizing and describing outputs of neuroimaging
experiments'. \emph{Scientific Data}, vol. 3.

Goscinski, W. J., P. McIntosh, U. C. Felzmann, A. Maksimenko, C. J.
Hall, T. Gureyev, D. Thompson, A. Janke, G. Galloway, N. E. B. Killeen,
P. Raniga, O. Kaluza, A. Ng, G. Poudel, D. Barnes, T. Nguyen, P.
Bonnington and G. F. Egan (2014). "The Multi-modal Australian ScienceS
Imaging and Visualisation Environment (MASSIVE) high performance
computing infrastructure: applications in neuroscience and
neuroinformatics research." \emph{Frontiers in Neuroinformatics} 8.

Halchenko, Y., Hanke, M., Poldrack, B., Meyer, K., Debanjum, Alteva, G.,
\ldots{} Feilong Ma. (2018). Datalad/Datalad 0.10.2. Zenodo.
https://doi.org/10.5281/zenodo.808846

Kennedy, D. N. (2018). Neuroimaging Neuroinformatics: Sample Size and
Other Evolutionary Topics. \emph{Neuroinformatics}, 16(2), 149--150.
\href{https://doi.org/10.1007/s12021-018-9379-8}{{https://doi.org/10.1007/s12021-018-9379-8}}

Marcus D. S. et al. (2007), `The extensible neuroimaging archive
toolkit'. \emph{Neuroinformatics}, vol. 5, pp. 11--33.

Moore, D., Budd, R., \& Wright, W. (2008). \emph{Professional Python
Frameworks: Web 2.0 Programming with Django and Turbogears}. John Wiley
\& Sons.

Paszke, A., Chintala, S., Collobert, R., Kavukcuoglu, K., Farabet, C.,
Bengio, S., ... \& Mariethoz, J. Pytorch: Tensors and dynamic neural
networks in python with strong gpu acceleration, may 2017.

Raymond, E. S. (1999). The Cathedral and the Bazaar. O'Reilly Media.
ISBN 1-56592-724-9. pp. 30.

Scott, A., Courtney, W., Wood, D., De la Garza, R., Lane, S., Wang, R.,
... \& Calhoun, V. D. (2011). COINS: an innovative informatics and
neuroimaging tool suite built for large heterogeneous datasets.
\emph{Frontiers in neuroinformatics}, \emph{5}, 33.

Smith S. M. et al. (2004): Advances in functional and structural MR
image analysis and implementation as FSL. \emph{NeuroImage} vol. 23, pp.
S208--S219.

Sudlow C. et al. (2015) UK Biobank: An Open Access Resource for
Identifying the Causes of a Wide Range of Complex Diseases of Middle and
Old Age. \emph{PLoS Medicine};12:e1001779.

Schreiber J. et al (2018) `Using a Multi-Petaflop Supercomputer for
Pushing Neuroimaging Analytics to the Next Level', In: \emph{Proceedings
of Organisation for Human Brain Mapping 2018}, Singapore, Singapore

Tournier, J. D., Calamante, F., \& Connelly, A. (2010). Improved
probabilistic streamlines tractography by 2nd order integration over
fibre orientation distributions. In \emph{Proceedings of the
international society for magnetic resonance in medicine} (Vol. 18, p.
1670).

Tournier J.D. et al. (2012): `MRtrix: Diffusion tractography in crossing
fiber regions'. \emph{International Journal of Imaging Systems and
Technology}, vol. 22, pp. 53--66.

Thompson P.M. et al. (2014): `The ENIGMA Consortium: large-scale
collaborative analyses of neuroimaging and genetic data'. \emph{Brain
Imaging and Behavior}, vol. 8, pp.153--182.

Van Essen D.C. et al. (2012): `The Human Connectome Project: A data
acquisition perspective'. \emph{NeuroImage}, vol. 62, pp. 2222--2231.

Ward, P. G. D., Ferris, N. J., Raniga, P., Dowe, D. L., Ng, A. C. L.,
Barnes, D. G., \& Egan, G. F. (2018). Combining images and anatomical
knowledge to improve automated vein segmentation in MRI. NeuroImage,
165, 294--305.
\href{https://doi.org/10.1016/J.NEUROIMAGE.2017.10.049}{{https://doi.org/10.1016/J.NEUROIMAGE.2017.10.049}}

White, T. (2012). \emph{Hadoop: The definitive guide}. O'Reilly Media,
Inc..

Yacoub, S. M., \& Ammar, H. H. (2004). \emph{Pattern-oriented analysis
and design: composing patterns to design software systems}.
Addison-Wesley Professional.

\hypertarget{supplementary-material}{%
\section{Supplementary Material}\label{supplementary-material}}

\includegraphics[width=5.88542in,height=6.21875in]{media/image24.png}

\textbf{Figure S.1} - First section of the definition of the
\emph{ArcanaPaper} Study class. ArcanaPaper implements the analysis
performed for this manuscript. ArcanaPaper is a \emph{MultiStudy} with
two sub-studies, a T2*-weighted/T1-weighted multi-study and a dMRI
study. Two default parameters of the global tracking pipeline in the
dMRI study are overridden to reduce the number of tracks created for
visualisation purposes. The class inherits from the
\emph{ImageDisplayMixin} class to include methods to display slices of
the derived images.

\includegraphics[width=5.89583in,height=5.38542in]{media/image25.png}\textbf{Figure
S.2 -} Method in ArcanaPaper class to generate Figure 11 of this
manuscript. SWI, QSM and vein mask derivatives are generated on demand
if they don't already exist in the repository by the \emph{data} method.
\emph{display\_slice\_panel} and \emph{save\_or\_show} methods from the
\emph{nianalysis.plot.ImageDisplayMixin} base class are used to display
the generated filesets.

\includegraphics[width=5.83333in,height=4.58333in]{media/image31.png}

\textbf{Figure S.3 -} Method in ArcanaPaper class to generate Figure 12
of this manuscript. FA and ADC derivatives are generated on demand if
they don't already exist in the repository by the \emph{data} method.
\emph{display\_slice\_panel} and \emph{save\_or\_show} methods from the
\emph{nianalysis.plot.ImageDisplayMixin} base class are used to display
the generated filesets.

\includegraphics[width=5.98958in,height=5.76042in]{media/image26.png}

\textbf{Figure S.4 -} Method in ArcanaPaper class to generate Figure 13
of this manuscript. Global tracks and FA are derived on demand if they
don't already exist in the repository by the \emph{data} method. Uses
the \emph{display\_tcks\_with\_mrview} method in the
\emph{nianalysis.plot.ImageDisplayMixin} class to display streamlines on
a background of a fractional anisotropy (FA) map using MRtrix's
\emph{mrview} command.

\includegraphics[width=6.125in,height=6.78125in]{media/image29.png}

\textbf{Figure S.5 -} Instantiation of the specific study class to a
dataset stored on the local system. Images for Figures 11, 12 and 13 of
this manuscript are generated by eponymous methods of the study. Entries
in the study's data specification are matched to data in the repository
using \emph{FilesetSelector} objects. The use of \emph{LinearProcessor}
specifies that derivatives are derived using a single process on the
local system. Equivalent figures can be generated for alternative
datasets by specifying a different repository and inputs.

>>>>

%%%%%%%%%%%%%%%%%%%%%%% file template.tex %%%%%%%%%%%%%%%%%%%%%%%%%
%
% This is a general template file for the LaTeX package SVJour3
% for Springer journals.          Springer Heidelberg 2010/09/16
%
% Copy it to a new file with a new name and use it as the basis
% for your article. Delete % signs as needed.
%
% This template includes a few options for different layouts and
% content for various journals. Please consult a previous issue of
% your journal as needed.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
% First comes an example EPS file -- just ignore it and
% proceed on the \documentclass line
% your LaTeX will extract the file if required
\begin{filecontents*}{example.eps}
%!PS-Adobe-3.0 EPSF-3.0
%%BoundingBox: 19 19 221 221
%%CreationDate: Mon Sep 29 1997
%%Creator: programmed by hand (JK)
%%EndComments
gsave
newpath
  20 20 moveto
  20 220 lineto
  220 220 lineto
  220 20 lineto
closepath
2 setlinewidth
gsave
  .4 setgray fill
grestore
stroke
grestore
\end{filecontents*}
%
\RequirePackage{fix-cm}
%
%\documentclass{svjour3}                     % onecolumn (standard format)
%\documentclass[smallcondensed]{svjour3}     % onecolumn (ditto)
\documentclass[smallextended]{svjour3}       % onecolumn (second format)
%\documentclass[twocolumn]{svjour3}          % twocolumn
%
\smartqed  % flush right qed marks, e.g. at end of proof
%
\usepackage{graphicx}
\usepackage{hyperref}
\usepackage{longtable}
\usepackage{booktabs}
%
% \usepackage{mathptmx}      % use Times fonts if available on your TeX system
%
% insert here the call for the packages your document requires
%\usepackage{latexsym}
% etc.
%
% please place your own definitions here and don't use \def but
% \newcommand{}{}
%
% Insert the name of "your journal" with
% \journalname{myjournal}
%
\begin{document}

\title{A comprehensive framework to capture the arcana of neuroimaging
analysis%\thanks{Grants or other notes
%about the article that should go on the front page should be
%placed here. General acknowledgments should be placed at the end of the article.}
}

%\titlerunning{Short form of title}        % if too long for running head

\author{
	Thomas G. Close \and
	Phillip G. D. Ward  \and
	Francesco Sforazzini  \and
	Wojtek Goscinski  \and
	Zhaolin Chen  \and
	Gary F. Egan  \and
}

%\authorrunning{Short form of author list} % if too long for running head

\institute{F. Author \at
              first address \\
              \email{tom.close@monash.edu}           %  \\
%             \emph{Present address:} of F. Author  %  if needed
           \and
           S. Author \at
              second address
}

\date{Received: date / Accepted: date}
% The correct dates will be entered by the editor

\maketitle

\begin{abstract}
Insert your abstract here. Include keywords, PACS and mathematical
subject classification numbers as needed.
\keywords{First keyword \and Second keyword \and More}
% \PACS{PACS code1 \and PACS code2 \and more}
% \subclass{MSC code1 \and MSC code2 \and more}
\end{abstract}

\section{Introduction}
\label{intro}

Despite the availability of well-established neuroimaging analysis
packages (Cox 1996; Smith et. al. 2004; Friston et. al. 2007; Tournier
et. al. 2012), the arcana of neuroimaging analysis is substantial due to
the range of available tools, tuneable parameters, and imaging sequences
involved (Cusack et. al. 2015). The distribution of complete
``end-to-end'' workflows, from acquired data to publication results, is
necessary for routine reproduction because of the effort required to
accurately exactly reimplement such analyses (Kennedy 2018). It is also
difficult to adapt existing workflows to new studies without detailed
knowledge of their design. Therefore, flexible, portable and complete
workflows are important to promote reproduction and code reuse in
neuroimaging research.

@@

\section{Methods}
\label{methods}

\subsection{Framework overview}
\label{framework-overview}

@@

%\includegraphics[width=3.55074in,height=3.16146in]{media/image23.png}

@@

%\includegraphics[width=6.27083in,height=3.15278in]{media/image33.png}

@@

\subsection{Analysis design: Study classes}
\label{analysis-design-study-classes}

@@

\subsubsection{Data and parameter specification
tables}
\label{data-and-parameter-specification-tables}

@@

%\includegraphics[width=5.74851in,height=6.07813in]{media/image27.png}

@@

\subsubsection{Workflow design}
\label{workflow-design}

@@

%\includegraphics[width=5.33854in,height=4.21623in]{media/image35.png}

@@

The syntax for workflow graph construction in Arcana is inspired by the
proposed format for Nipype v2.0
(\href{https://github.com/nipy/nipype/issues/2539}{https://github.com/nipy/nipype/issues/2539}),
and will be updated as Nipype v2.0 is developed and upstream
functionality becomes available. Workflow nodes are created from Nipype
interfaces using the \emph{Pipeline.add(name, interface)} method of the
Pipeline should be used. Once created, the inputs of the node can be set
explicitly via the node's \emph{inputs} attribute, connected to other
nodes with the \emph{Pipeline.connect(out\_node, out\_node\_output,
in\_node, in\_node\_input)} method, or connected to inputs of the
pipeline. Pipeline inputs and outputs are connected to nodes using the
\emph{Pipeline.add\_input(spec\_name, node, node\_input)} and
\emph{Pipeline.add\_output(spec\_name, node, node\_output)} methods,
respectively.

@@

%\includegraphics[width=6.27083in,height=2in]{media/image7.png}

@@

\subsubsection{Extension and specialisation by class inheritance}
\label{extension-and-specialisation-by-class-inheritance}

@@

\subsubsection{Implementing multi-modal
studies}
\label{implementing-multi-modal-studies}

@@

%\includegraphics[width=3.86429in,height=4.70313in]{media/image20.png}

@@

%\includegraphics[width=6.27083in,height=4.69444in]{media/image21.png}

@@

%\includegraphics[width=6.27083in,height=3.94444in]{media/image36.png}\textbf{Figure 8} - Example application of Study class to a dataset stored in an XNAT
%repository. Once the Study object has been initialised potential
%derivatives of the Study can be requested, and will be generated and
%stored in the repository if already present.

@@

\subsubsection{Study inputs}
\label{study-inputs}

@@

\subsubsection{Processor modules}
\label{processor-modules}

@@

\section{Results}
\label{results}

@@

%\includegraphics[width=3.82849in,height=6.85938in]{media/image28.png}

@@

%\includegraphics[width=4.29167in,height=7.43818in]{media/image32.png}

@@

%\includegraphics[width=6.228in,height=4.72396in]{media/image22.png}

@@

%\includegraphics[width=6.27083in,height=4.18056in]{media/image34.png}

@@

%\includegraphics[width=6.27083in,height=2.09722in]{media/image30.png}

@@

\section{Discussion}
\label{discussion}

@@

\section{Conclusion}
\label{conclusion}

@@

% Your text comes here. Separate text sections with
% \section{Section title}
% \label{sec:1}
% Text with citations \cite{RefB} and \cite{RefJ}.
% \subsection{Subsection title}
% \label{sec:2}
% as required. Don't forget to give each section
% and subsection a unique label (see Sect.~\ref{sec:1}).
% \paragraph{Paragraph headings} Use paragraph headings as needed.
% \begin{equation}
% a^2+b^2=c^2
% \end{equation}

% For one-column wide figures use
\begin{figure}
% Use the relevant command to insert your figure file.
% For example, with the graphicx package use
  \includegraphics{example.eps}
% figure caption is below the figure
\caption{Please write your figure caption here}
\label{fig:1}       % Give a unique label
\end{figure}
%
% For two-column wide figures use
\begin{figure*}
% Use the relevant command to insert your figure file.
% For example, with the graphicx package use
  \includegraphics[width=0.75\textwidth]{example.eps}
% figure caption is below the figure
\caption{Please write your figure caption here}
\label{fig:2}       % Give a unique label
\end{figure*}
%
% For tables use
\begin{table}
% table caption is above the table
\caption{Please write your table caption here}
\label{tab:1}       % Give a unique label
% For LaTeX tables use
\begin{tabular}{lll}
\hline\noalign{\smallskip}
first & second & third  \\
\noalign{\smallskip}\hline\noalign{\smallskip}
number & number & number \\
number & number & number \\
\noalign{\smallskip}\hline
\end{tabular}
\end{table}

%\begin{acknowledgements}
%If you'd like to thank anyone, place your comments here
%and remove the percent signs.
%\end{acknowledgements}

% BibTeX users please use one of
%\bibliographystyle{spbasic}      % basic style, author-year citations
%\bibliographystyle{spmpsci}      % mathematics and physical sciences
%\bibliographystyle{spphys}       % APS-like style for physics
%\bibliography{}   % name your BibTeX data base

% Non-BibTeX users please use
\begin{thebibliography}{}
%
% and use \bibitem to create references. Consult the Instructions
% for authors for reference list style.
%
\bibitem{RefJ}
% Format for Journal Reference
Author, Article title, Journal, Volume, page numbers (year)
% Format for books
\bibitem{RefB}
Author, Book title, page numbers. Publisher, place (year)
% etc
\end{thebibliography}

\end{document}
% end of file template.tex
